### 2012-05-16 inst/examples/reckless_driver.Rmd
reckless driver scenario

`ro cache=TRUE, tidy=FALSE, warning=FALSE, comment=NA, message=FALSE, fig.width=10, fig.height=10, refresh=1 or`

@@

# Calculating the value of information
 * author Carl Boettiger, <cboettig@gmail.com>
 * license: CC0

@@

``` {r  simulate }
sigma_g <- 0.15    # Noise in population growth
sigma_m <- 0.15     # noise in stock assessment measurement
sigma_i <- 0.15     # noise in implementation of the quota
z_g <- function() rlnorm(1,  0, sigma_g) # mean 1
z_m <- function() rlnorm(1,  0, sigma_m) # mean 1
z_i <- function() rlnorm(1,  0, sigma_i) # mean 1
sims_known <- lapply(1:100, function(i){
  ForwardSimulate(f, pars, x_grid, h_grid, x0=K, opt$D, z_g, z_m, z_i, profit)
})
````

@@

``` {r }
sigma_g <- 0.15    # Noise in population growth
z_g <- function() rlnorm(1,  0, sigma_g) # mean 1
z_m <- function() 1 
z_i <- function() 1
````
Find the transition matrix

``` {r }
SDP_Mat <- determine_SDP_matrix(f, pars, x_grid, h_grid, sigma_g )
````

``` {r }
opt <- find_dp_optim(SDP_Mat, x_grid, h_grid, OptTime=25, xT=0, 
                     profit, delta=0.05, reward=0)
````

@@

``` {r }
sigma_g <- 0.15    # Noise in population growth
sigma_m <- 0.15     # noise in stock assessment measurement
sigma_i <- 0.15     # noise in implementation of the quota
z_g <- function() rlnorm(1,  0, sigma_g) # mean 1
z_m <- function() rlnorm(1,  0, sigma_m) # mean 1
z_i <- function() rlnorm(1,  0, sigma_i) # mean 1

@@

``` {r }
sigma_g <- 0.15    # Noise in population growth
sigma_m <- 0.15     # noise in stock assessment measurement
z_g <- function() rlnorm(1,  0, sigma_g) # mean 1
z_m <- function() rlnorm(1,  0, sigma_m) # mean 1
z_i <- function() 1
````

Find the transition matrix.  Use the simulation method to account for the extra uncertainties

``` {r }
require(snowfall) 
sfInit(parallel=TRUE, cpu=16)
SDP_Mat <- SDP_by_simulation(f, pars, x_grid, h_grid, z_g, z_m, z_i, reps=999)
````

``` {r }
opt <- find_dp_optim(SDP_Mat, x_grid, h_grid, OptTime=25, xT=0, 
                     profit, delta=0.05, reward=0)
````

@@

``` {r }
sigma_g <- 0.15    # Noise in population growth
sigma_m <- 0.15     # noise in stock assessment measurement
sigma_i <- 0.15     # noise in implementation of the quota
z_g <- function() rlnorm(1,  0, sigma_g) # mean 1
z_m <- function() rlnorm(1,  0, sigma_m) # mean 1
z_i <- function() rlnorm(1,  0, sigma_i) # mean 1
sims_gm <- lapply(1:100, function(i){
  ForwardSimulate(f, pars, x_grid, h_grid, x0=K, opt$D, z_g, z_m, z_i, profit)
})
````

@@

``` {r }
sigma_g <- 0.15    # Noise in population growth
sigma_m <- 0.15     # noise in stock assessment measurement
sigma_i <- 0.15     # noise in implementation of the quota
z_g <- function() rlnorm(1,  0, sigma_g) # mean 1
z_m <- function() rlnorm(1,  0, sigma_m) # mean 1
z_i <- function() rlnorm(1,  0, sigma_i) # mean 1
````

Find the transition matrix.  Use the simulation method to account for the extra uncertainties

``` {r }
SDP_Mat <- SDP_by_simulation(f, pars, x_grid, h_grid, z_g, z_m, z_i, reps=999)
````

``` {r }
opt <- find_dp_optim(SDP_Mat, x_grid, h_grid, OptTime=25, xT=0, 
                     profit, delta=0.05, reward=0)
````

>>>>

`ro cache=TRUE, tidy=FALSE, warning=FALSE, comment=NA, message=FALSE, fig.width=10, fig.height=10, refresh=1, cache.path="reckless_driver/" or`

@@

# Reckless Driver Scenario

Manager assumes the world is basically deterministic, performs in a variety of scenarios of an increasingly uncertain world.

 * author Carl Boettiger, <cboettig@gmail.com>
 * license: CC0

@@

``` {r  simulate }
sigma_g <- 0.01    # Noise in population growth
z_g <- function() rlnorm(1,  0, sigma_g) # mean 1
z_m <- function() 1 
z_i <- function() 1 
sims_known <- lapply(1:100, function(i){
  ForwardSimulate(f, pars, x_grid, h_grid, x0=K, opt$D, z_g, z_m, z_i, profit)
})
````

@@

@@

``` {r }
sigma_g <- 0.15    # Noise in population growth
z_g <- function() rlnorm(1,  0, sigma_g) # mean 1
z_m <- function() 1
z_i <- function() 1

@@

```

@@

``` {r }
sigma_g <- 0.15    # Noise in population growth
sigma_m <- 0.15     # noise in stock assessment measurement
z_g <- function() rlnorm(1,  0, sigma_g) # mean 1
z_m <- function() rlnorm(1,  0, sigma_m) # mean 1
z_i <- function() 1 
sims_gm <- lapply(1:100, function(i){
  ForwardSimulate(f, pars, x_grid, h_grid, x0=K, opt$D, z_g, z_m, z_i, profit)
})
````

@@

### 2012-05-16 inst/examples/value_of_stochasticity.Rmd
reckless driver scenario

`ro cache=TRUE, tidy=FALSE, warning=FALSE, comment=NA, message=FALSE, fig.width=10, fig.height=10, cache.path="value_of_information/" or`

@@

``` {r }
sigma_g <- 0.15    # Noise in population growth
z_g <- function() rlnorm(1,  0, sigma_g) # mean 1
````
Find the transition matrix

@@

Simulate.  The real world doesn't have as much uncertainty as we do in our knowledge of the state.

``` {r }
sigma_g <- 0.05    # Noise in population growth
z_g <- function() rlnorm(1,  0, sigma_g) # mean 1
sims_g <- lapply(1:100, function(i){
  ForwardSimulate(f, pars, x_grid, h_grid, x0=K, opt$D, z_g, profit=profit)
})
````

@@

``` {r }
sigma_g <- 0.15    # Noise in population growth
sigma_m <- 0.15     # noise in stock assessment measurement
z_g <- function() rlnorm(1,  0, sigma_g) # mean 1
z_m <- function() rlnorm(1,  0, sigma_m) # mean 1
z_i <- function() 1
````

@@

``` {r }
sigma_g <- 0.05    # Noise in population growth
z_g <- function() rlnorm(1,  0, sigma_g) # mean 1
z_m <- function() 1
z_i <- function() 1
sims_gm <- lapply(1:100, function(i){
  ForwardSimulate(f, pars, x_grid, h_grid, x0=K, opt$D, z_g, z_m, z_i, profit)
})
````

@@

``` {r }
sigma_g <- 0.15    # Noise in population growth
sigma_m <- 0.15     # noise in stock assessment measurement
sigma_i <- 0.15     # noise in implementation of the quota
z_g <- function() rlnorm(1,  0, sigma_g) # mean 1
z_m <- function() rlnorm(1,  0, sigma_m) # mean 1
z_i <- function() rlnorm(1,  0, sigma_i) # mean 1
````

@@

``` {r }
sigma_g <- 0.05    # Noise in population growth
z_g <- function() rlnorm(1,  0, sigma_g) # mean 1
z_m <- function() 1
z_i <- function() 1
sims_gmi <- lapply(1:100, function(i){
  ForwardSimulate(f, pars, x_grid, h_grid, x0=K, opt$D, z_g, z_m, z_i, profit)
})
````

>>>>

`ro cache=TRUE, tidy=FALSE, warning=FALSE, comment=NA, message=FALSE, fig.width=10, fig.height=10, cache.path="value_of_stochasticity/" or`

@@

``` {r }
sigma_g <- 0.15    # Noise in population growth
sigma_m <- 0.0     # noise in stock assessment measurement
sigma_i <- 0.0     # noise in implementation of the quota
z_g <- function() rlnorm(1,  0, sigma_g) # mean 1
z_m <- function() rlnorm(1,  0, sigma_m) # mean 1
z_i <- function() rlnorm(1,  0, sigma_i) # mean 1
````
Find the transition matrix

@@

``` {r }
sims_g <- lapply(1:100, function(i){
  ForwardSimulate(f, pars, x_grid, h_grid, x0=K, opt$D, z_g, z_m, z_i, profit)
})
````

@@

``` {r }
sigma_m <- 0.15     # noise in stock assessment measurement
z_m <- function() rlnorm(1,  0, sigma_m) # mean 1
````

@@

``` {r }
sims_gm <- lapply(1:100, function(i){
  ForwardSimulate(f, pars, x_grid, h_grid, x0=K, opt$D, z_g, z_m, z_i, profit)
})
````

@@

``` {r }
sigma_i <- 0.15     # noise in implementation of the quota
z_i <- function() rlnorm(1,  0, sigma_i) # mean 1
````

@@

``` {r }
sims_gmi <- lapply(1:100, function(i){
  ForwardSimulate(f, pars, x_grid, h_grid, x0=K, opt$D, z_g, z_m, z_i, profit)
})
````
